LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-07 main.tex
Convert PDF figures to version 1.5
Update keywords

% FIXME Some figures use PDF version 1.6, PDFLaTeX default is 1.5
\pdfoptionpdfminorversion 6

@@

\begin{keyword}
% FIXME Match keywords and PACS and MSC classifications
% FIXME Consult previous publications to find keywords
Lagrangian coherent structures \sep Mathematical software \sep Dynamical systems \sep Invariant manifolds \sep Mixing

% FIXME Verify these classifications, http://www.aip.org/pacs
\PACS 47.10.Fg \sep 47.27.De \sep 47.11.-j

% FIXME Verify these classifications http://www.ams.org/msc/msc2010.html
\MSC[2010] 37N10 \sep 37B25 \sep 97N80
\end{keyword}

>>>>

@@

\begin{keyword}
Lagrangian coherent structures \sep Mathematical software \sep Non-autonomous dynamical systems \sep Invariant manifolds \sep Mixing \sep Transport barriers \sep Fluid dynamics \sep Ocean surface flows

\PACS 47.10.Fg \sep 47.27.De \sep 47.11.-j \sep 05.45.-a \sep 47.51.+a \sep 47.54.-r \sep 92.10.hf \sep 93.30.Qn \sep 92.10.ab \sep 92.10.Ty \sep 92.10.ak \sep 92.10.A-

\MSC[2010] 37N10 \sep 37B25 \sep 97N80 \sep 37C60 \sep 37B55 \sep 70H33 \sep 76F25
\end{keyword}
